Modelling the Retinotectal projection - can competition provide a stopping mechanism?

### 2021-07-15 paper/paper.tex
WIP on paper methods and a simplification of axon-axon interactions

In this model, the signal transmitted when a ligand binds to a receptor on a
growth cone can lead to one of two effects; the signal may induce an
attraction towards the ligand-expression region or a repulsion away from it.
%
For axon-tectum interactions, we implement attraction as a climbing of the
tectal ligand expression gradient and repulsion as gradient descent.
%
To determine the strength of the effect we assume a purely linear receptor
binding model, and set the movement of the growth cone to be $\sum_i \pm
r_i \times \grad l_i$.

For axon-axon interactions, attraction causes a movement along a vector
between two axons causing them to move closer together; repulsion cause the
opposite effect.

>>>>

In this model, the signal transmitted when a ligand binds to a receptor on a
growth cone can lead to one of two effects; the signal may induce an
attraction towards the ligand-expression region or a repulsion away from it.
%
For axon-tectum interactions, we implemented attraction as a climbing of the
tectal ligand expression gradient and repulsion as gradient descent.
%
To determine the strength of the effect we assumed a purely linear receptor
binding model, and set the chemotactic movement vector of the growth cone to
be
%
\begin{equation}
\mathbf{G} = \sum_i^N D_i r_i \nabla l_i
\end{equation}
%
where $r_i$ is the receptor expression for ligand-receptor pair $i$,
$\nabla l_i$ is the gradient of the ligand expression and $D_i$ denotes the
direction of the interaction induced when a molecule of $l_i$ binds to
$r_i$. $D_i$ takes the value -1 for a repulsive interaction or 1 for an
attractive interaction.

For axon-axon interactions, attraction causes a movement along a vector,
$\mathbf{x}_{b_0}$, between two axons causing them to move closer together;
repulsion causes the opposite effect. The interaction, $\mathbf{I}$, is given
by
%
\begin{equation}
\mathbf{I} = \sum_b \mathbf{x}_{b_0} Q(d_{b0})
\end{equation}
%
where $Q(d_{b0})$ is the signalling strength between two growth cones, given by
%
\begin{equation}
Q(d_{b0}) = \begin{cases}
     \sum_i^N D_i l_i r_i    & d_{b0} < 2r \\
     0 & d_{b0} \geq 2r
     \end{cases}
\end{equation}
